skater: An R package for SNP-based Kinship Analysis, Testing, and Evaluation

### 2021-07-15 paper/paper.Rmd
affiliations

author:
  - name: Stephen D. Turner
    affiliation: "1"
  - name: V.P. Nagraj
    affiliation: "1"
  - name: Matthew Scholz
    affiliation: "1"
  - name: Shakeel Jessa
    affiliation: "1"
  - name: Carlos Acevedo
    affiliation: "1"
  - name: Jianye Ge
    affiliation: "2"
  - name: August Woener
    affiliation: "2"
  - name: Bruce Budowle
    affiliation: "2"

address:
  - code: 1
    address: Signature Science, LLC., Charlottesville, Virginia, 22911, USA.
  - code: 2
    address: University of North Texas Health Science Center, Fort Worth, Texas, 76107, USA.

>>>>

author:
  - name: Stephen D. Turner
    affiliation: "1"
  - name: V.P. Nagraj
    affiliation: "1"
  - name: Matthew Scholz
    affiliation: "1"
  - name: Shakeel Jessa
    affiliation: "1"
  - name: Carlos Acevedo
    affiliation: "1"
  - name: Jianye Ge
    affiliation: "2,3"
  - name: August Woener
    affiliation: "2,3"
  - name: Bruce Budowle
    affiliation: "2,3"

address:
  - code: 1
    address: Signature Science, LLC., Charlottesville, Virginia, 22911, USA.
  - code: 2
    address: Center for Human Identification, University of North Texas Health Science Center, 3500 Camp Bowie Blvd., Fort Worth, TX, 76107, USA
  - code: 3
    address: Department of Microbiology, Immunology, and Genetics, University of North Texas Health Science Center, 3500 Camp Bowie Blvd., Fort Worth, TX, 76107, USA
